Leadership across cultures and contexts: an exploratory analysis

### 2020-05-15 Response to reviewers.Rmd

We now more clearly motivate our discussion of the functions of leaders and link discussions to these sources and ideas. 
**The Wofford study (lines 214-233) and GLOBE study reminds me of the vast array of descriptive models in leadership/managerial studies- transactional vs. transformational leadership and their sub-components being one of the most popular. So what should a reader make of this literature, with respect to evolution of leadership in small-scale societies? Do bureaucracies, formal legal systems, formal education-based skills, and large inequalities in remuneration limit universality of descriptive models from leadership/managerial studies? I'd be more explicit on this in the introduction.**

We now include additional discussion of managerial frameworks of leader behavior and highlight recent approaches that are more conducive to coupling with evolutionary and anthropological/psychological approaches.

**For the discussion section: how does your own descriptive modeling of leadership in traditional societies agree or not with Wofford or other models from large-scale societies?**

In our revision, we initially included a paragraph in our concluding statement interpreting our overall findings in reference to Wofford's and GLOBE study results, i.e., attempting (albeit briefly) to tie in our (non-WEIRD) results to relevant findings from WEIRD settings. However, following all revisions and our expanded analyses the maintext was over 20,000 words. We therefore decided to move essentially all of our detailed review of leaderhsip in WEIRD settings to the SI. Now, this conclusion statement would be out of place. We do make a few very brief and general statements comparing non-WEIRD and WEIRD leadership, but direct readers to the SI for details.

@@

**Can you control for phylogeny (e.g. linguistic affinity). See Minocher et al. 2019 in Evolution and Human Behavior. It may be that covariation you detect between qualities and leader functions is driven by shared cultural history more than direct causal relationship between qualities and leader functions.**

We appreciate this point, however as mentioned above, we did not incorporate proper phylogenetic controls. The PSF as a stratified random sample provide some safeguards against effects of non-independence, although not perfectly. We do now include significant additional analyses more systematically including and reporting continental region and subsistence strategy effects as control measures. We also now report the GLMM for each of our researcher-coded variables which includes random effects for author nested within culture and we report on possible sources of biases in the SI.

**Can you report text records pertaining to male vs. female leadership by subsistence type (lines 966-982)?**

We now report that the majority of female leader-exclusive text records were from horticulturalists (76%) and provide a table of text records by leader sex and subsistence in the SI.

### 2020-05-15 leadership_across_cultures_contexts.Rmd
Edits in reviewer. Added to SI.
Moved shaman stuff into plan.R

loadd(all_data)
loadd(all_data2)
loadd(all_study_vars)
loadd(coercive_plot)
loadd(df_func)
loadd(df_qual)
loadd(features)
loadd(feature_models)
loadd(feature_models_aic)
loadd(features_support_cult)
loadd(follower_bc_ratio)
loadd(follower_benefits_txt)
loadd(follower_costs_txt)
loadd(follower_benefits_cult)
loadd(follower_costs_cult)
loadd(functions_support_cult)
loadd(functions_support_txt)
loadd(highstatus_plot)
loadd(leader_bc_ratio)
loadd(leader_benefits_txt)
loadd(leader_benefits_cult)
loadd(leader_costs_txt)
loadd(leader_costs_cult)
loadd(m_lpca_func)
loadd(m_lpca_qual)
loadd(m_pvclust_func)
loadd(m_pvclust_qual)
loadd(multi_aic)
loadd(multi_allvars)
# loadd(p_heatmap_groups)
# loadd(p_heatmap_region)
# loadd(p_heatmap_sex)
# loadd(p_heatmap_subsis)
loadd(p_heatmap_feature_subsis)
loadd(p_heatmap_feature_region)
loadd(p_heatmap_feature_sex)
loadd(p_heatmap_feature_groups)
loadd(plot_costs_benefits)
loadd(plot_elastic_status)
loadd(plot_elastic_coercive)
loadd(plot_features_support)
loadd(plot_func_qual)
loadd(plot_pubdate)
loadd(qualities_support_cult)
loadd(qualities_support_txt)

@@

```{r fivefold, fig.width=10, fig.cap="The intersections of evidence for our five basic elements of leadership among all text records (an 'upset' plot) [@gehlenborg2019]. Horizontal bars (left): The total number of text records in each element. Black dots: has evidence. Gray dots: does not have evidence. Vertical bars (top): The number of text records in that intersection (with lower limit set at 3). Red: The number of text records involving shamans or leaders with supernatural qualities. "}

>>>>

loadd(all_data)
loadd(all_data2)
loadd(all_study_vars)
loadd(coercive_plot)
loadd(df_func)
loadd(df_qual)
loadd(df_shaman)
loadd(features)
loadd(feature_models)
loadd(feature_models_aic)
loadd(features_support_cult)
loadd(follower_bc_ratio)
loadd(follower_benefits_txt)
loadd(follower_costs_txt)
loadd(follower_benefits_cult)
loadd(follower_costs_cult)
loadd(functions_support_cult)
loadd(functions_support_txt)
loadd(highstatus_plot)
loadd(leader_bc_ratio)
loadd(leader_benefits_txt)
loadd(leader_benefits_cult)
loadd(leader_costs_txt)
loadd(leader_costs_cult)
loadd(m_lpca_func)
loadd(m_lpca_qual)
loadd(m_pvclust_func)
loadd(m_pvclust_qual)
loadd(multi_aic)
loadd(multi_allvars)
# loadd(p_heatmap_groups)
# loadd(p_heatmap_region)
# loadd(p_heatmap_sex)
# loadd(p_heatmap_subsis)
loadd(p_heatmap_feature_subsis)
loadd(p_heatmap_feature_region)
loadd(p_heatmap_feature_sex)
loadd(p_heatmap_feature_groups)
loadd(plot_costs_benefits)
loadd(plot_elastic_shamanism)
loadd(plot_elastic_status)
loadd(plot_elastic_coercive)
loadd(plot_features_support)
loadd(plot_func_qual)
loadd(plot_pubdate)
loadd(plot_shamanism_text)
loadd(qualities_support_cult)
loadd(qualities_support_txt)

@@

```{r fivefold, fig.width=10, fig.cap="The intersections of evidence for our five basic elements of leadership among all text records (an 'upset' plot) [@gehlenborg2019]. Horizontal bars (left): The total number of text records in each element. Black dots: has evidence. Gray dots: does not have evidence. Vertical bars (top): The number of text records in that intersection (with lower limit set at 3). Red: The number of text records involving shamans or leaders with supernatural qualities."}
